\documentclass{article}
\title{Solution 1}
\author{@kyrylo}

\begin{document}

\section*{Solutions to assignment 1}

\section{}

Elimination of the ambiguity of the {\it The man saw the woman with a telescope}
sentence can be avoided with these two natural sounding equivalents:

\begin{enumerate}
\item The man with a telescope saw the woman.
\item The man saw the woman carrying a telescope.
\end{enumerate}

\section{}

This is how you can remove the ambiguity, retainging the brevity of a typical
headline:

\begin{enumerate}
\item Sisters reunited in checkout line at Safeway after ten years
\item Large hole appears in High Street. City authorities are investinating it
\item Mayor says bus passengers should wear belts
\end{enumerate}

\section{}

{\it No head injury is too trivial to ignore} can be paraphrased as {\it None
  of head injuries are too trivial to ignore} or {\it Every head injury is vital
  and can't be ignored}.

\section{}

Since ``Fire'' has multiple different meanings, a user of this word must supply
a context. In case of the following notice the context is clear: {\it In case of
  fire, do not use elevator}. However, without context this phrase can have
another meaning.  It can mean that in case of any fire (such as a cigarette
lighter or even shooting) you are not advised to use the elevator. So, it can be
paraphrased as {\it Do not use elevator, if the building is on fire}.

\section{}

The sentence does not make a true statement, because the page is already not
blank. If it was really blank, then it wouldn't have anything printed on it.
The purpose of making such a statement is to show to the reader that the page
is not the result of an error at the printing house, but an intentional deed.

It can be reformulated as this: {\it No material on this page}.

\section{}

\begin{enumerate}
\item Pakistan talks with Taliban
\item \dots
\item \dots
\end{enumerate}

\section{}

{\it The temperature is hot today} is a very inaccurate mark of the temperature,
since every human being perceives it differently.``hot'' for a resident
of Siberia, could be the same as``mild'' or ``normal'' for a resident of Africa.

\section{}

We show that not every number of the form $N = (p_1 \cdot p_2 \cdot p_3 \cdot
\dots \cdot p_n) + 1$ is prime, where $p_1, p_2, p_3, \cdots, p_n, \cdots$ is
the list of all prime numbers. If $N$ divided by any of $p_i$ factors leaves the
remainder of 1, it is a composite number. Otherwise, it is a prime number.

\section*{JUST FOR FUN}
\setcounter{section}{0}

\section{}

Context: robotics.

The robot said ``I have a message for you and, and, and, and'', and then he
broke.

\section{}

Context: recursion.

Provide a context and a sentence within that context, where the words and, or,
and, or, and occur in that order, with no other word between them.

\end{document}
