\documentclass{article}
\title{Solution 8}
\author{@kyrylo}

\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{centernot}
\usepackage{amsfonts}

\begin{document}

\section*{Solutions to assignment 8}

\section{}

Theorem: ``There are integers $m, n$ such that $m^2 + mn + n^2$ is a perfect
square''.
\\
Proof: Let $A(m, n)$ denote ``$m^2 + mn + n^2$ is a perfect square''.
Hence, we're proving $(\exists m \in \mathbb{Z})(\exists n \in \mathbb{Z})[A(m, n)]$
Let's pick arbitrarily $m = 1, n = 0$. We are proving $A(1, 0)$, which is
$1^2 + 1 \cdot 0 + 0^2 = 1 + 0 + 0 = 1$. The acquired number $1$ is a perfect square and this
proves $A(m, n)$.

\section{}

Theorem: ``For any positive integer $m$ there is a positive integer $n$ such
that $mn + 1$ is a perfect square''
\\
Proof: Let $A(m, n)$ denote ``$mn + 1$ is a perfect square". Hence, we're
proving $(\forall m \in \mathbb{Z})(\exists n \in \mathbb{Z})[A(m, n)]$. Let $m$
be an arbitrary positive integer. Set $n = m + 2$. Then $mn + 1 = m \cdot (m +
2) + 1$ can be expressed as
\\
$m \cdot (m + 2) + 1 = m^2 + 2m + 1 = m^2 + m + m + 1 = (m + 1)(m + 1) = (m + 1)^2$
\\
This proves that $(m + 1)^2$ is a perfect square.

\section{}

Theorem: ``There is a quadratic $f(n) = n^2 + bn + c$ with positive integer
coefficients $b, c$, such that $f(n)$ is composite for all positive integers
$n$.''
\\
Proof: we are proving
\\
$(\exists b \in \mathbb{Z})(\exists c \in \mathbb{Z})(\forall n \in
\mathbb{Z})[(c > 0) \wedge (b > 0) \wedge (n > 0) \wedge \neg Prime(n^2 + bn +
c)]$ Let $b = 1, c = 2$, then $f(n) = n^2 + 2n + 1 = (n + 1)^2$. Since $(n +
1)^2$ always gives a perfect square, it means that the result is composite,
because it can be divided by $n + 1$ (and prime numbers can be divided only by 1 and
by itself). For example: $n = 36, f(n) = (n + 1)^2 = (36 + 1)^2 = 37^2 =
1369$. So, $1369 / (n + 1)= 1369 / (36 + 1) = 37$.

\section{}

Theorem: ``If every even natural number greater than 2 is a sum of two primes
(the Goldbach Conjecture), then every odd natural number greater than 5 is a sum
of three primes.''
\\
Proof: let $A(x)$ denote that $x$ can be expressed as a sum of two primes and
let $B(x)$ denote that $x$ can be expressed as a sum of three primes. We're
proving $(\forall x \in \mathbb{N})[x > 2 \wedge Even(x) \implies A(x)] \implies
(\forall y \in \mathbb{N})[y > 5 \wedge Odd(y) \implies B(y)]$.  Assume that
$(\forall x \in \mathbb{N})[x > 2 \wedge Even(x) \implies A(x)]$ is true. Since
the next odd number after 5 is 7, we can state that $y \geq 7$ and since the
next even number after 2 is 4 we can state that $x \geq 4$. The difference between
7 and 4 is 3, which is a prime number. So by the Goldbach Conjecture we get
$y - 3 = p + q$, where $p, q$ are prime numbers. Thus, $y = p + q + 3$ is a proof.

\section{}

Theorem: ``The sum of the first $n$ odd numbers is equal to $n^2$.''
\\
Proof: by mathematical induction.
\\
For $n = 1$ the first and the last number is 1, so $1^2 = 1$, which is true.
\\
For $n = 2$ the first odd numbers are $1, 3$ and their sum is 4, so $2^2 = 4$,
which is also true.
\\
For $n = 3$ the first odd numbers are $1, 3, 5$ and their sum is 9, so $3^2 =
9$, which is also true.
\\
Let $A(n)$ be the statement $\sum\limits_{i=1}^n i = n^2$. Assume the identity
holds for $n$, i.e. $A(n)$. Let's deduce $A(n + 1)$. So, $(n + 1)^2 = n^2 + 2n +
1$.
\\
?
\end{document}
